Pesticides in small agricultural streams in Germany

### 2016-08-12 article.tex
intro

National monitoring programs are setup for determination and surveillance of the chemical and ecological status of surface, ground and drinking water.
These monitoring programs produce large amounts of data, which possibly can also be used to answer other questions.
In Germany monitoring programs are setup by the federal states in compliance with the Water Framework Directive \citep{quevauviller_water_2008} and further state specific needs.
However, currently there is no curated national-wide compilation of this data.

Small water bodies are important refuges of biodiversity \citep{davies_comparison_2008} and enabling downstream colonisation of polluted streams \citep{liess_analyzing_2005}.
At the same time they may be exposed to a high risk of pesticide contamination from adjacent agricultural areas and low dilution effects \citep{liess_determination_1999}.
Although small streams comprise a major fraction of streams \citep{nadeau_hydrological_2007} relatively little is know about their chemical and ecological status.

>>>>

National monitoring programs are setup for determination and surveillance of the chemical and ecological status of surface, ground and drinking water.
These monitoring programs produce large amounts of data, which possibly can also be used to answer other questions.
In Germany monitoring programs are setup independently by the federal states in compliance with the Water Framework Directive \citep{quevauviller_water_2008} and additional state specific needs.
However, currently there is no curated national-wide compilation of this data available.

\citet{malaj_organic_2014} analysed data supplied to the European Union in the context of the Water Framework Directive (WFD). 
However, this reflects only a small part of data from national scale monitoring programs.

Small water bodies are important refuges of biodiversity \citep{davies_comparison_2008} and enable downstream colonisation of polluted streams \citep{liess_analyzing_2005}.
At the same time they may be exposed to a high risk of pesticide contamination from adjacent agricultural areas and low dilution effects \citep{liess_determination_1999}.
Although small streams comprise a major fraction of streams \citep{nadeau_hydrological_2007} relatively little is know about their chemical and ecological status.
